Graph Based Clustering

### 2022-09-30 reports/04_clustering.Rmd

```{r setup, include=FALSE}
knitr::opts_chunk$set(fig.width = 6.6929133858, 
                      message    = FALSE,
                      warning    = FALSE)
#setwd("/Users/vilkal/work/Brolidens_work/Projects/broliden_5325/reports")
```

```{r Load data, message=FALSE, warning=FALSE}
##################
# LOAD LIBRARIES #
##################
#setwd("/Users/vilkal/work/Brolidens_work/Projects/Gabriella_repo/reports/rmarkdown/manuscript")
suppressWarnings({suppressMessages({suppressPackageStartupMessages({
  library(tidyverse)
  library(igraph)
  library(rafalib)
  #remotes::install_github("czarnewski/niceRplots",upgrade = "always",force = T)
  library(niceRplots)
})  })  })

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(fig.width = 6.6929133858,
                      results    = "hold",
                      message    = FALSE,
                      warning    = FALSE)
#setwd("/Users/vilkal/work/Brolidens_work/Projects/broliden_5325/reports")
```

```{r Load data, message=FALSE, warning=FALSE}
##################
# LOAD LIBRARIES #
##################
#setwd("/Users/vilkal/work/Brolidens_work/Projects/Gabriella_repo/reports/rmarkdown/manuscript")
suppressWarnings({suppressMessages({suppressPackageStartupMessages({
  library(tidyverse)
  library(igraph)
  library(rafalib)
  library(RANN)
  library(uwot)
  #remotes::install_github("czarnewski/niceRplots",upgrade = "always",force = T)
  library(niceRplots)
})  })  })
